Supporting Non-Functional Requirements for Services Software Process: An MDD Approach

### 2013-10-14 SOFSEM2014/FinalVersion/pisodm.tex
begin corrections --martin

@@

$\pi$SOD-M proposes the generation of a set of models at different abstraction levels, as
well as transformations between these models.
$\pi$SOD-M models represent both the functional aspects of the application as well as its non-functional constraints. 
Constraints are restrictions that must be verified during the execution of the application. 
An example of this is the requirement of the user's authentication for executing some system functions.

>>>>

Policies are associated to service operations and combine \textit{constraints} and \textit{reactive recovery actions}.
Constraints are restrictions that must be verified during the execution of the application. 
An example of this is the requirement of authentication for executing some of the system functions. 
Failure to verify the constraints will trigger exceptions to execute their corresponding recovery actions.

In this context, we provide concepts at different levels of abstraction for expressing business rules of a process as policies (to implement existing NFP protocols).

@@

$\pi$SOD-M proposes the generation of a set of models at different abstraction levels, as
well as transformations between these models.
$\pi$SOD-M models represent both the functional aspects of the application as well as their non-functional behaviour.
